Multi-task learning in Computer Vision

### 2020-05-31 3-Image-classification.tex
More images. Fix tables. Add new stuff.
Add more minor fixes.

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/imagenet_parameters.png}
\caption{Number of parameters in popular ImageNet classifiers. Figure from \citep{efficientNet}.\label{fig:params}}
\end{figure}

@@

The ResNet block architecture allows for the blocks to learn the identity function more efficiently by trying to learn the residual function instead of the direct mapping. The residual can be learned by adding the unchanged weights of an earlier layer to the output of some transformations on it.
The residual block is shown in Figure 3.2.
Normally a neural network layer learns the mapping between ${x}$ and ${y}$ using a function ${H(x)}$, but by the same token, we can learn a residual transformation.
Learning these residuals using the identity mapping skip-connections is the revolutionary idea introduced by the ResNet.
Since these residual connections are only connections, they do not require extra parameters to be learned and are free in terms of learnable parameters.
The residual transformation is
\[{F(x) = H(x) - x}\] \noindent where ${H}$ is the mapping of two or more network layers. Both of these approaches should approximate the same functions; the difference is in how easy it is for the network to learn. Learning a transformation of ${F(x) = 0}$ would intuitively seem easier for a neural network than learning ${F(x) = x}$. As can be seen from the success of the ResNets compared to non-residual networks, this is what allows for creating very deep networks. If the transformation changes the input size, a matrix ${W}$ is necessary to map the input to the same dimensions, generating the final formula for a residual block. \[y = F(x, \{W_i\}) + W_s x\] \noindent where $W_i$ and $W_s$ are the the weight matrices to be applied to x.

>>>>

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/imagenet-own.png}
\caption{Number of parameters in popular ImageNet classifiers. Figure adapted from \citep{efficientNet}.\label{fig:params}}
\end{figure}

@@

The ResNet block architecture allows for the blocks to learn the identity function more efficiently by trying to learn the residual function instead of the direct mapping. The residual can be learned by adding the unchanged weights of an earlier layer to the output of some transformations on it.
The residual block is shown in Figure 3.2.
Normally a neural network layer learns the mapping between ${x}$ and ${y}$ using a function ${H(x)}$, but by the same token, we can learn a residual transformation.
Learning these residuals using the identity mapping skip-connections is the revolutionary idea introduced by the ResNet.
Since these skip-connections are only connections and not extra layers, they do not require extra parameters that would need to be learned.
The residual transformation is
\[{F(x) = H(x) - x}\] \noindent where ${H}$ is the mapping of two or more network layers. Both of these approaches should approximate the same functions; the difference is in how easy it is for the network to learn. Learning a transformation of ${F(x) = 0}$ would intuitively seem easier for a neural network than learning ${F(x) = x}$. As can be seen from the success of the ResNets compared to non-residual networks, this is what allows for creating very deep networks. If the transformation changes the input size, a matrix ${W}$ is necessary to map the input to the same dimensions, generating the final formula for a residual block. \[y = F(x, \{W_i\}) + W_s x\] \noindent where $W_i$ and $W_s$ are the the weight matrices to be applied to x.

### 2020-05-31 7-Experiments.tex
Add more minor fixes.

One new thing that we noticed when training on this data set was that with too high learning rates, the experiments were not very repeatable.
It seems that in a multi-task setting, it is not easy to tell that the learning rate is too high.
In this case, when the learning process seemed to progress in a manner that we would call expected, the learning rate might actually be too high.
With a slightly too high learning rate, it seemed like it is relatively random, whether the model reaches the best weights.
Most likely, the sampling ratios matter here quite a lot, but with the same sampling ratios and a slightly too high learning rate, there didn't seem to be a guarantee that anything close to the best model would be reached.
Maybe this has something to do with the large variance in the size of the datasets.
With more dynamic sampling ratios, the problems might solve themselves, as then some tasks would hopefully not get stuck at low accuracies.
We noticed here the same thing as in the leaves experiment that a long training process that slowly approaches the optimum seems to produce the best results in the end consistently.
Maybe this means that finding the intersection that can solve all the tasks optimally is relatively small and easy to overshoot with too large learning rates.
Similarly, with incorrect sampling ratios, the model would never be able to reach the weights needed for the shared optimal solution.

>>>>

One new thing that we noticed when training on this data set was that with too high learning rates, the experiments were not very repeatable.
It seems that in a multi-task setting, it is not easy to tell that the learning rate is too high.
In this case, when the learning process seemed to progress in a manner that we would call expected, the learning rate might actually be too high.
With a slightly too high learning rate, it seemed like it is relatively random, whether the model reaches the best weights.
Most likely, the sampling ratios matter here quite a lot, but with the same sampling ratios and a slightly too high learning rate, there didn't seem to be a guarantee that anything close to the best model would be reached.
Maybe this has something to do with the large variance in the size of the datasets.
With more dynamic sampling ratios, the problems might solve themselves, as then some tasks would hopefully not get stuck at low accuracies.
We noticed here the same thing as in the leaves experiment that a long training process that slowly approaches the optimum seems to produce the best results in the end consistently.
Maybe this means that finding the intersection that can solve all the tasks optimally is relatively small and easy to overshoot with too large learning rates.
Similarly, with incorrect sampling ratios, the model would never be able to reach the weights needed for the shared optimal solution.
To deal with the imbalanced classes, we also tried to add an exponent to the loss like in the focal loss, though it is unsure if it was useful or not.
But in theory, it should allow for the network to learn more from the cases where it is unsure.
Also, it would be yet another parameter to tune, as it is hard to say what exactly the exponent should be for the best results.

### 2020-05-31 __latexindent_temp.tex
Add more minor fixes.

In the end, what we learned is that the success of multi-task learning some tasks can't be pre-determined currently, and some expensive experimentation is needed to arrive at the best multi-task architecture.  
Thus, multi-task learning can be considered as a trade-off of training time complexity for inference-time benefits in accuracy and speed.

>>>>

In all of our experiments, we could have spent more time on them to do more trials trying over different parameters and combinations of parameters.
Maybe by doing more thorough and systematic testing, it could be possible to evaluate exactly the effect of tuning a specific parameter.
Doing all the experiments would take a long time, and it is questionable whether the results would generalize to all problems.
The fact is that there are too many things that could be tuned, so it is difficult to determine which parameter should be tested.

Multi-task learning is a significant paradigm for creating large machine learning systems.
As it isn't really scalable, nor does it really make any sense to try to solve every task separately in a system that would be called intelligent.
For example, Andrej Karpathy, the Director of AI at Tesla, has given multiple talks on how they apply multi-task learning and how it is an instrumental part of their convolutional models \citep{karpathy}.
The problems he describes their teams tackle are the same problems that we have encountered and tried to solve in this thesis.
Like deciding what tasks should share and picking the correct sampling ratios are some of the problems Karpathy brings up as some of the most significant issues in training their models.
It does make sense that a camera-based self-driving car is one of the largest current multi-task learning applications as it is a problem that benefits from all the boons of multi-task learning we have covered.
It is important to have small models for running inference in constrained environments faster than single-task counterparts.
By sharing weights between tasks that have been specially picked in a way that they can augment each other makes it easier to learn new tasks and improve performance on the existing ones.
Having separate datasets for each task allows for the easy creation of new tasks in the model irrespective of others.
The ability to modify the loss weights and task sampling ratios allows for focusing on the critical tasks that are not allowed to fail.
So, while it likely is more difficult to train a model that solves all the tasks together, it is most likely unavoidable.
Single-task models that would solve the same tasks with the same real-time requirements would likely have to be so small that they would be unusable.
These are the kinds of problems where it is impossible to avoid using multi-task learning. 
With the correct techniques, it is possible to create systems that can reliably augment people's abilities.

In the end, what we learned is that the success of creating multi-task models out of some tasks can't be pre-determined currently. 
Some expensive experimentation is needed to arrive at the best multi-task architecture and to find the optimal parameters to train the model.  
Thus, multi-task learning can be considered as a trade-off of training time complexity for inference-time benefits in accuracy and speed.
